PANCHANGE_analysis

### 2020-08-19 PANCHANGE_analysis.Rmd
add ocir means

```{r}
dat.long %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder) %>%
  summarise(
    gad_base_retro = mean(gad.diff_score_base_retro, na.rm = T),
    gad_prepan_retro = mean(gad.diff_score_prepan_retro, na.rm = T),
    gad_prepan_base = mean(gad.diff_score_prepan_base, na.rm = T),
    phq_base_retro = mean(phq.diff_score_base_retro, na.rm = T),
    phq_prepan_retro = mean(phq.diff_score_prepan_retro, na.rm = T),
    phq_prepan_base = mean(phq.diff_score_prepan_base, na.rm = T)
    )
```

>>>>

```{r}
dat.long %>%
  filter(Diagnosis == 1) %>%
  group_by(Disorder) %>%
  summarise(
    gad_base_retro = mean(gad.diff_score_base_retro, na.rm = T),
    gad_prepan_retro = mean(gad.diff_score_prepan_retro, na.rm = T),
    gad_prepan_base = mean(gad.diff_score_prepan_base, na.rm = T),
    phq_base_retro = mean(phq.diff_score_base_retro, na.rm = T),
    phq_prepan_retro = mean(phq.diff_score_prepan_retro, na.rm = T),
    phq_prepan_base = mean(phq.diff_score_prepan_base, na.rm = T),
    ocir_base_retro = mean(ocir.diff_score_base_retro, na.rm = T),
    ocir_prepan_retro = mean(ocir.diff_score_prepan_retro, na.rm = T),
    ocir_prepan_base = mean(ocir.diff_score_prepan_base, na.rm = T)
    )
```
